---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

latest_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vT_L3UBRsdzfI0_6AQBs_ewY3KrL2oovzqpelbsp5Titc522yjXFtdoy-QCKyEAEvQFrlm_pj353F3l/pub?gid=852631793&single=true&output=csv")

latest_data <- latest_data |>
  rename(
    time_of_day = 2,
    passenger_count = 3,
    crowdedness = 4,
    behaviour = 5)
```

```{css}
h2 {
  color: #004c99;
  font-family: Arial;}
```

## Bus Crowdedness and Passenger Behavior

This dynamic report summarises observations collected from bus trips to and from the University of Auckland over a 2-week period. The data includes the time of day, approximate number of passengers, perceived crowdedness, and what most passengers were doing during the trip.

```{r}
mean_passengers <- mean(latest_data$passenger_count)

most_common_crowdedness <- latest_data$crowdedness |>
  table() |>
  which.max() |>
  names()
```

Across all observations, the average number of passengers was **`r mean_passengers`**.

The most common crowdedness level was **`r most_common_crowdedness`**.

```{r}
ggplot(latest_data, aes(x = crowdedness)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Crowdedness levels", x = "Crowdedness", y = "Count")
```

```{r}
ggplot(latest_data, aes(x = time_of_day)) +
  geom_bar(fill = "darkorange") +
  labs(title = "Observations by time of day", x = "Time of day", y = "Count")
```

```{r}
ggplot(latest_data, aes(x = behaviour)) +
  geom_bar(fill = "seagreen") +
  labs(title = "What people were doing", x = "Behaviour", y = "Count")
```
